Structural Breaks in Inflation Dynamics within the European Monetary Union

### 2011-03-11 pkg/paper/Paper/draft.Rnw
"Draft" -> "Paper" directory
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/glogis@78 b679b2f7-6539-45d0-a605-5ddcb976cde9

## For the creation of the tables
## <<tabelle, eval=FALSE>>=
root_dir <- do.call("file.path", as.list(head(strsplit(getwd(), .Platform$file.sep)[[1]], -1)))
if(!file.exists(file.path(root_dir, "Analysis", "Austria.rda"))) {
setwd(file.path(root_dir, "Analysis"))
## run results3 (with dummy creation for sales periods)
Sweave("results3.Rnw")
setwd(file.path(root_dir, "Draft"))
}

@@

  setwd(file.path(root_dir, "Analysis"))
	save(hicp, hicp_glmean, diff, file = "glmean.rda")
	setwd(file.path(root_dir, "Draft"))

@@

% appendix HINTER reference
\begin{appendix}\ref{app}

>>>>

## For the creation of the tables
## <<tabelle, eval=FALSE>>=
root_dir <- do.call("file.path", as.list(head(strsplit(getwd(), .Platform$file.sep)[[1]], -1)))
if(!file.exists(file.path(root_dir, "Analysis", "Austria.rda"))) {
setwd(file.path(root_dir, "Analysis"))
## run results3 (with dummy creation for sales periods)
Sweave("results3.Rnw")
setwd(file.path(root_dir, "Paper"))
}

@@

  setwd(file.path(root_dir, "Analysis"))
	save(hicp, hicp_glmean, diff, file = "glmean.rda")
	setwd(file.path(root_dir, "Paper"))

@@

% appendix HINTER reference
\begin{appendix}\label{app}
